---
title: "Appendix"
author: "Julianna Szabo"
date: "12/30/2020"
output: html_document
---

# Ln transformation

## Occupancy percentage 

### Level - level regression
```{r, echo=FALSE}
df %>% 
  ggplot(aes(x = capacity_filled, y = revenue_per_att)) +
  geom_point() +
  geom_smooth(method="loess")+
  labs(x = "Occupancy percentage",y = "Revenue per attendant") +
  theme_bw()
```

### Log - level regression
```{r, echo=FALSE}
df %>% 
  ggplot(aes(x = ln_capacity_filled, y = revenue_per_att)) +
  geom_point() +
  geom_smooth(method="loess")+
  labs(x = "ln (Occupancy percentage)",y = "Revenue per attendant") +
  theme_bw()
```

### Level - log regression
```{r, echo=FALSE}
df %>% 
  ggplot(aes(x = capacity_filled, y = ln_revenue_per_att)) +
  geom_point() +
  geom_smooth(method="loess")+
  labs(x = "Occupancy percentage",y = "ln (Revenue per attendant)") +
  theme_bw()
```

### Log - log regression
```{r, echo=FALSE}
df %>% 
  ggplot(aes(x = ln_capacity_filled, y = ln_revenue_per_att)) +
  geom_point() +
  geom_smooth(method="loess")+
  labs(x = "ln (Occupancy percentage)",y = "ln (Revenue per attendant)") +
  theme_bw()
```

## Percentage of potential profit 

### Level - level regression
```{r, echo=FALSE}
df %>% 
  ggplot(aes(x = percentage_of_poss_profit, y = revenue_per_att)) +
  geom_point() +
  geom_smooth(method="loess")+
  labs(x = "Percentage of potential profit",y = "Revenue per attendant") +
  theme_bw()
```

### Log - level regression
```{r, echo=FALSE}
df %>% 
  ggplot(aes(x = ln_percentage_of_poss_profit, y = revenue_per_att)) +
  geom_point() +
  geom_smooth(method="loess")+
  labs(x = "ln (Percentage of potential profit)",y = "Revenue per attendant") +
  theme_bw()
```

### Level - log regression
```{r, echo=FALSE}
df %>% 
  ggplot(aes(x = percentage_of_poss_profit, y = ln_revenue_per_att)) +
  geom_point() +
  geom_smooth(method="loess")+
  labs(x = "Percentage of potential profit",y = "ln (Revenue per attendant)") +
  theme_bw()
```

### Log - log regression
```{r, echo=FALSE}
df %>% 
  ggplot(aes(x = ln_percentage_of_poss_profit, y = ln_revenue_per_att)) +
  geom_point() +
  geom_smooth(method="loess")+
  labs(x = "ln (Percentage of potential profit)",y = "ln (Revenue per attendant)") +
  theme_bw()
```

## Number of performances 

### Level - level regression
```{r, echo=FALSE}
df %>% 
  ggplot(aes(x = num_of_performances, y = revenue_per_att)) +
  geom_point() +
  geom_smooth(method="loess")+
  labs(x = "Number of performances",y = "Revenue per attendant") +
  theme_bw()
```

### Log - level regression
```{r, echo=FALSE}
df %>% 
  ggplot(aes(x = ln_num_of_performances, y = revenue_per_att)) +
  geom_point() +
  geom_smooth(method="loess")+
  labs(x = "ln (Number of performances)",y = "Revenue per attendant") +
  theme_bw()
```

### Level - log regression
```{r, echo=FALSE}
df %>% 
  ggplot(aes(x = num_of_performances, y = ln_revenue_per_att)) +
  geom_point() +
  geom_smooth(method="loess")+
  labs(x = "Number of performances",y = "ln (Revenue per attendant)") +
  theme_bw()
```

### Log - log regression
```{r, echo=FALSE}
df %>% 
  ggplot(aes(x = ln_num_of_performances, y = ln_revenue_per_att)) +
  geom_point() +
  geom_smooth(method="loess")+
  labs(x = "ln (Number of performances)",y = "ln (Revenue per attendant)") +
  theme_bw()
```





# Regression modes

## Regression 1 - Simple linear regression
```{r, echo=FALSE}
reg1 <- lm_robust( ln_revenue_per_att ~ capacity_filled , data = df,  se_type = "HC2" )
summary( reg1 )
ggplot( data = df, aes( x = capacity_filled, y = ln_revenue_per_att ) ) + 
  geom_point( color='blue') +
  geom_smooth( method = lm , color = 'red' ) +
  labs(x = "Occupancy percentage",y = "ln (Revenue per attendant)")
```

## Regression 2 - Quadratic (linear) regression
```{r, echo=FALSE}
reg2 <- lm_robust( ln_revenue_per_att ~ capacity_filled + capacity_filled_sq , data = df )
summary( reg2 )
ggplot( data = df, aes( x = capacity_filled, y = ln_revenue_per_att ) ) + 
  geom_point( color='blue') +
  geom_smooth( formula = y ~ poly(x,2) , method = lm , color = 'red' ) +
  labs(x = "Occupancy percentage",y = "ln (Revenue per attendant)")
```

## Regressipn 3 - Piecewise linear spline regression

Using 0.5 as a cutof point
```{r, echo=FALSE}
# Define the cutoff for occupancy
cutoff <- 0.5
# Use simple regression with the lspline function
reg3 <- lm_robust(ln_revenue_per_att ~ lspline( capacity_filled , cutoff ), data = df )
summary( reg3 )
ggplot( data = df, aes( x = capacity_filled, y = ln_revenue_per_att ) ) + 
  geom_point( color='blue') +
  geom_smooth( formula = y ~ lspline(x,cutoff) , method = lm , color = 'red' ) +
  labs(x = "Occupancy percentage",y = "ln (Revenue per attendant)")
```


## Regression 4 - Weighted linear regression, where  weights = percentage of total revenue
```{r, echo=FALSE}
reg4 <- lm_robust(ln_revenue_per_att ~ capacity_filled, data = df , weights = percentage_of_poss_profit)
summary( reg4 )

ggplot(data = df, aes(x = capacity_filled, y = ln_revenue_per_att)) +
  geom_point(data = df, aes(size=percentage_of_poss_profit),  color = 'blue', shape = 16, alpha = 0.6,  show.legend=F) +
  geom_smooth(aes(weight = percentage_of_poss_profit), method = "lm", color='red')+
  labs(x = "Occupancy percentage",y = "ln (Revenue per attendant)")
```

## Regression 5 - Weighted linear regression, where weights = number of performances
```{r, echo=FALSE}
reg5 <- lm_robust(ln_revenue_per_att ~ capacity_filled, data = df , weights = num_of_performances)
summary( reg4 )

ggplot(data = df, aes(x = capacity_filled, y = ln_revenue_per_att)) +
  geom_point(data = df, aes(size=num_of_performances),  color = 'blue', shape = 16, alpha = 0.6,  show.legend=F) +
  geom_smooth(aes(weight = num_of_performances), method = "lm", color='red')+
  labs(x = "Occupancy percentage",y = "ln (Revenue per attendant)")
```

# Model Comparison
```{r, echo=FALSE}
data_out <- "/Users/Terez/OneDrive - Central European University/Data_Analysis_02/DA2_Assignment_2/out/"
htmlreg( list(reg1 , reg2 , reg3 , reg4 ,reg5 ),
         type = 'html',
         custom.model.names = c("Occupancy percentage - linear","Occupancy percentage - quadratic",
                                "Occupancy percentage - PLS",
                                "Occupancy percentage- weighted (profit) linear",
                                "Occupancy percentage- weighted (number of per) linear"),
         caption = "Modelling Revenue per attendant on Occupancy percentage for different shows",
         file = paste0( data_out ,'model_comparison.html'), include.ci = FALSE)
```
Looks like these models with mainly one variable are not a great fit for the data. Therefore, I will include additional variables to try and get a better fit. Further, it looks like the original use of "Number of Performances" has no impact so I will try and create a dummy variable and use that instead. I will use 0 for any show that had less than one year of performances so less than 8*52 (416) and one for those that have had more.

```{r, echo=FALSE}
df <- df %>% mutate( num_of_performances_d = 1*(num_of_performances>416))
```


## Additional models

Check if it becomes better if one of the weights are included as variables

```{r, echo=FALSE}
reg6 <-  lm_robust( ln_revenue_per_att ~ capacity_filled + percentage_of_poss_profit, data = df,  se_type = "HC2" )
summary( reg6 ) 

reg7 <-  lm_robust( ln_revenue_per_att ~ capacity_filled + as.factor(num_of_performances_d), data = df,  se_type = "HC2" )
summary( reg7) 

reg8 <-  lm_robust( ln_revenue_per_att ~ capacity_filled + percentage_of_poss_profit + as.factor(num_of_performances_d), data = df,  se_type = "HC2" )
summary( reg8 ) 

reg9 <-  lm_robust( ln_revenue_per_att ~ capacity_filled + percentage_of_poss_profit + as.factor(num_of_performances_d) + as.factor(show_type), data = df,  se_type = "HC2" )
summary( reg9 ) 
```


## Explore again

```{r, echo=FALSE}
data_out <- "/Users/Terez/OneDrive - Central European University/Data_Analysis_02/DA2_Assignment_2/out/"
htmlreg( list(reg1 , reg2 , reg3 , reg4 , reg5 , reg6, reg7, reg8),
         type = 'html',
         custom.model.names = c("Occupancy percentage - linear","Occupancy percentage - quadratic",
                                "Occupancy percentage - PLS",
                                "Occupancy percentage- weighted (profit) linear",
                                "Occupancy percentage- weighted (number of per) linear",
                                "Occupancy percentage + Profit - linear",
                                "Occupancy percentage + number of per - linear",
                                "Occupancy percentage + profit + number of per - linear"),
         caption = "Modelling Revenue per attendant on Occupancy percentage for different shows",
         file = paste0( data_out ,'model_comparison.html'), include.ci = FALSE)
```



