---
title: "Broadway data analysis"
author: "Julianna Szabo"
date: "12/23/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Research question

How did the Revenue per attendant change over time?
Main aim is prediction

## Data

The data quatily is very good especially for time series data. I have data from 1990 to 2016 for all shows running, so it is very representative. Since my x is time, there is no measurement error. There may be some classical error measurement in y because of inflation or miss counting, but nothing too unusual.
I will use using Revenue / Attendant, where Revenue is measured as the gross revenue of the show per week, and attendants which are measured as total number of people who attended the show that week.

My x variable will be time using the full date (weekly)
My y variable will be Revenue / Attendant which I will calculate based on revenue and attendant

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
